The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-30 paper.tex
update

  The density of clumpy disk can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk:\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the pressure equilibrium condition implies that the temperature of disk is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

@@

  Motivated by these observations, we simulate three different inclined angles,\
  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.

  All three cases with different inclined angles share the same injection parameters:\
  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
  the CR energy density $e_{\text{CR}}=??$,\
  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
  along the symmetric axis of cylinder.

@@

  Jet power Eddington luminosity

  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{pc}^{3}$ is\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.

>>>>

  The density of clumpy disk can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk, i.e.,\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the pressure equilibrium within the clumpy disk implies that the temperature of disk is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

@@

  Motivated by these observations, we simulate three cases with different inclined angles,\
  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.

  All three cases with different inclined angles share the same injection parameters:\
  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
  the CR energy density $e_{\text{CR}}=??$,\
  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
  along the symmetric axis of cylinder.\
  The jet power is thus $3.2\times 10^{42}$ erg/s, resulting in the Eddington ratio 0.008.

@@

  The bipolar jets are constantly ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.
